STAT 253 Final Project

### 2022-10-12 Final_Project_Work_HW2.Rmd
HW3 work

```{r}
library(readr)
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
```

@@

>>>>

```{r}
library(readr)
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
head(imdb_top_1000)
```

@@

```{r}
lm_spec_gam <-
  linear_reg() %>%
  set_engine(engine = 'lm') %>%
  set_mode('regression')

full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    step_rm(Series_Title, Released_Year, Overview,
            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross)

spline_rec <- full_rec %>%
     step_ns(Runtime, deg_free = edf) %>% 
     step_ns(IMDB_Rating, deg_free = edf) %>%
     step_ns(No_of_Votes, deg_free = edf)

movie_wf <- workflow() %>%
    add_model(lm_spec) %>%
    add_recipe(full_rec)

spline_wf <- workflow() %>%
    add_model(lm_spec) %>%
    add_recipe(spline_rec)

fit_resamples(
    movie_wf,
    resamples = data_cv8, # cv folds
    metrics = metric_set(mae,rmse,rsq)                     
) %>% collect_metrics()
```
